Test

### 2023-04-04 S3_run_simulations_original_not_last.Rmd
refactoring

```{r}
#cleanup memory
gcstuff <- gc(verbose=FALSE); rm(gcstuff);
```

@@

```{r}
expName <- "_orig_nl"
slopeDir <- paste0(baseSlopeDir, expName)
fitDir <- paste0(baseFitDir, expName)

dir.create(slopeDir)
dir.create(fitDir)

@@

## fit all trios of models in parallel (for linux only, but easy to adjust for other OS):
pbmcapply::pbmclapply(scenarios_to_do, function(scenario) {
  fits <- fit_life_histories(scenario = scenario,
                             birth_level_data = data_births_monthly)
  save(fits, file = paste0(fitDir,"/fits_", scenario, "_obs.rda"), compress = "xz")

  rm(fits)
  }, mc.cores = min(c(length(scenarios_to_do), nb_cores)), mc.preschedule = FALSE)

for (scenario in scenarios_to_do) {

@@

   slopes_under_scenario <- simulate_slopes_for_GOF(N_replicates_level1 = 200L,
                                                    N_replicates_level2 = 49L,
                                                    birth_level_data = data_births_monthly,
                                                    life_history_fits = fits,
                                                    scenario = scenario,
                                                    nb_cores = nb_cores,
                                                    timeout = timeout,
                                                    .log = TRUE, lapply_pkg = "pbmcapply",
                                                    verbose = list(fit = TRUE, simu = FALSE))
   rm(fits)
   name_obj <- paste0("slopes_under_", scenario)
   assign(name_obj, value = slopes_under_scenario)
   save(list = name_obj, file = paste0(slopeDir, name_obj, ".rda"))
   rm(list = name_obj) # remove the object behind the name!
   rm(slopes_under_scenario, scenario, name_obj) # remove the object directly
   gc_stuff <- gc(verbose = FALSE)
}

## Combine simulated slopes:

@@

fig5 <- draw_fig_5(all_slopes, width = 1)
fig5Fname <- paste0("./exports/fig5_", expName, ".")
ggplot2::ggsave(file = paste0(fig5Fname, "pdf"), width = 88, height = 70, units = "mm")
ggplot2::ggsave(file = paste0(fig5Fname, "png"), width = 88, height = 70, units = "mm")

## test scenarios (table S13):

@@

write.csv(tableS13, file = paste0(fig5Fname, "csv"))

## computing time (for gof analysis):

### Estonain Data

```{r}
expName <- "_EE_nl"
slopeDir <- paste0(baseSlopeDir, expName)
fitDir <- paste0(baseFitDir, expName)

dir.create(slopeDir)
dir.create(fitDir)

data_births_monthly <- data_births_monthly_EE_not_last

## fit all trios of models in parallel (for linux only, but easy to adjust for other OS):
pbmcapply::pbmclapply(scenarios_to_do, function(scenario) {
  fits <- fit_life_histories(scenario = scenario,
                             birth_level_data = data_births_monthly)
  save(fits, file = paste0(fitDir,"/fits_", scenario, "_obs.rda"), compress = "xz")

  rm(fits)
  }, mc.cores = min(c(length(scenarios_to_do), nb_cores)), mc.preschedule = FALSE)

for (scenario in scenarios_to_do) {

   slopes_under_scenario <- simulate_slopes_for_GOF(N_replicates_level1 = 200L,
                                                    N_replicates_level2 = 49L,
                                                    birth_level_data = data_births_monthly,
                                                    life_history_fits = fits,
                                                    scenario = scenario,
                                                    nb_cores = nb_cores,
                                                    timeout = timeout,
                                                    .log = TRUE, lapply_pkg = "pbmcapply",
                                                    verbose = list(fit = TRUE, simu = FALSE))
   rm(fits)
   name_obj <- paste0("slopes_under_", scenario)
   assign(name_obj, value = slopes_under_scenario)
   save(list = name_obj, file = paste0(slopeDir, name_obj, ".rda"))
   rm(list = name_obj) # remove the object behind the name!
   rm(slopes_under_scenario, scenario, name_obj) # remove the object directly
   gc_stuff <- gc(verbose = FALSE)
}

## Combine simulated slopes:

fig5 <- draw_fig_5(all_slopes, width = 1)
fig5Fname <- paste0("./exports/fig5_", expName, ".")
ggplot2::ggsave(file = paste0(fig5Fname, "pdf"), width = 88, height = 70, units = "mm")
ggplot2::ggsave(file = paste0(fig5Fname, "png"), width = 88, height = 70, units = "mm")

## test scenarios (table S13):

write.csv(tableS13, file = paste0(fig5Fname, "csv"))

## computing time (for gof analysis):

>>>>

```{r}
#cleanup memory
gcstuff <- gc(verbose=FALSE); rm(gcstuff);

```{r}
cat("The current directory is: ", getwd())
```

@@

```{r make directories}
expName <- "_orig_nl"
slopeDir <- paste0(baseSlopeDir, expName)
fitDir <- paste0(baseFitDir, expName)

dir.create(slopeDir, recursive = T)
dir.create(fitDir, recursive = T)

@@

cat("Fits are saved in: ", fitDir)
```

```{r fit models}
## fit all trios of models in parallel (for linux only, but easy to adjust for other OS):
pbmcapply::pbmclapply(scenarios_to_do, function(scenario) {
  fits <- fit_life_histories(scenario = scenario,
                             birth_level_data = data_births_monthly)
  save(fits, file = paste0(fitDir,"/fits_", scenario, "_obs.rda"), compress = "xz")

  rm(fits)
  }, mc.cores = min(c(length(scenarios_to_do), nb_cores)), mc.preschedule = FALSE)
```

```{r run scenarios}
for (scenario in scenarios_to_do) {

@@

   slopes_under_scenario <- simulate_slopes_for_GOF(N_replicates_level1 = 200L,
                                                    N_replicates_level2 = 49L,
                                                    birth_level_data = data_births_monthly,
                                                    life_history_fits = fits,
                                                    scenario = scenario,
                                                    nb_cores = nb_cores,
                                                    timeout = timeout,
                                                    .log = TRUE, lapply_pkg = "pbmcapply",
                                                    verbose = list(fit = TRUE, simu = FALSE))
   rm(fits)
   name_obj <- paste0("slopes_under_", scenario)
   assign(name_obj, value = slopes_under_scenario)
   save(list = name_obj, file = paste0(slopeDir,"/", name_obj, ".rda"))
   rm(list = name_obj) # remove the object behind the name!
   rm(slopes_under_scenario, scenario, name_obj) # remove the object directly
   gc_stuff <- gc(verbose = FALSE)
}
```

```{r draw figure}
## Combine simulated slopes:

@@

fig5 <- draw_fig_5(all_slopes, width = 1)
fig5Fname <- paste0("./exports/fig5_", expName, ".")
ggplot2::ggsave(filename = paste0(fig5Fname, "pdf"), fig5,
                width = 88, height = 70, units = "mm")
fig5
```

```{r draw figures}
## test scenarios (table S13):

@@

writexl::write_xlsx(tableS13, paste0(fig5Fname, "xlsx"))
knitr::kable(tableS13)
```

```{r timing}
## computing time (for gof analysis):

### 2023-04-04 test.Rmd
refactoring

```{r cars}
knitr::kable(summary(cars))
```

## Including Plots
```{r}
library(ggplot2)
```

@@

```{r pressure, echo=FALSE}
ggplot(pressure, aes(x=temperature, y=pressure)) + geom_point()
```

>>>>

```{r cars}
testDir <- "./exports/test/"
knitr::kable(summary(cars))
dir.create(testDir, recursive = T)
writexl::write_xlsx(cars, "./exports/test/test_cars.xlsx")
```

## Including Plots

@@

```{r pressure, echo=FALSE}
ggplot2::ggplot(pressure, ggplot2::aes(x=temperature, y=pressure)) + ggplot2::geom_point()
```
